Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-08-27 manuscript/manuscript.tex
adding Binder link (fixes #137)
minor change [ci skip]

Should the user prefer not to use Anaconda, a manual installation via the pip installer is possible.
Alternatively, one can use the Binder service to view and run the tutorials online in any browser.

@@

\begin{figure}
\includegraphics{figure_5}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone: the Trp-1 SASA autocorrelation function yields a weak signal (a) which, however, can be enhanced if the system is prepared in the nonequilibrium condition $\mathcal{S}_1$ (b). The solid/orange lines denote the maximum likelihood MSM result; the dashed/blue lines and the the shaded areas indicate sample means and $95\%$ confidence intervals computed with a Bayesian sampling procedure.}
\label{fig:msm-exp-obs}
\end{figure}

>>>>

Should the user prefer not to use Anaconda, a manual installation via the pip installer is possible.
Alternatively, one can use the Binder service (\url{https://mybinder.org}) to view and run the tutorials online in any browser.

@@

\begin{figure}
\includegraphics{figure_5}
\caption{Example analysis of the conformational dynamics of a pentapeptide backbone: (a)~the Trp-1 SASA autocorrelation function yields a weak signal which, however, (b)~can be enhanced if the system is prepared in the nonequilibrium condition $\mathcal{S}_1$. The solid/orange lines denote the maximum likelihood MSM result; the dashed/blue lines and the the shaded areas indicate sample means and $95\%$ confidence intervals computed with a Bayesian sampling procedure.}
\label{fig:msm-exp-obs}
\end{figure}
